Linecharts

### 2021-07-02 analysis/linecharts.Rmd
feat: add plot MeldCategory vs mean std values

```{r linecharts_zlogmeanplot}
labv <- sort(grep("_[SECQ]$", colnames(zlog_data), value = TRUE))

@@

par(mar = c(7.1, 4.1, 4.1, 2.1))

@@

>>>>

```{r linecharts_zlogmeanplot_status}
labv <- sort(grep("_[SECQ]$", colnames(zlog_data), value = TRUE))

@@

par(mar = c(7.1, 4.1, 4.1, 2.1), cex = 0.5)

@@

# Compare Mean Zlog Values vs MeldCategory

```{r linecharts_zlogmeanplot_meld}
## divide data.frame by MELD
s <- split(zlog_data[labv], zlog_data$MeldCategory)

## calculate mean standardized lab values
s <- lapply(s, colMeans, na.rm = TRUE)
n <- length(s)
o <- order(s[[n]])

## comparison plot
col <- rev(palette.colors(n))

par(mar = c(7.1, 4.1, 4.1, 2.1), cex = 0.5)

plot(
    s[[n]][o], type = "b", pch = 20, lwd = 2, col = col[n],
    axes = FALSE, ann = FALSE
)
for (i in seq_len(n - 1)) {
    lines(s[[i]][o], type = "b", pch = 20, lwd = 2, col = col[i])
}
legend(
    "bottomright",
    legend = names(s),
    col = col, lwd = 2, pch = 20, bty = "n"
)
title(
    main = "MELD Category vs Mean Standardized Laboratory Values", adj = 0
)
title(xlab = "Laboratory Measurements", adj = 1L, line = 5)
title(ylab = "Mean Standardized Values", adj = 1L)
r <- range(unlist(s))
axis(
    2, at = seq(from = floor(r[1]), to = ceiling(r[2])),
    lwd.ticks = 0, col = "#808080"
)
axis(
    1, at = seq_along(o), labels = names(s[[n]][o]), las = 2,
    lwd.ticks = 0L, col = "#808080"
)
abline(h = 0, col = "#808080", lty = 2)
par(old.par)
```
